\LaTeX\ Author Guidelines for 3DIMPVT Proceedings

### 2013-05-02 masters/body/assets/3dimpvt/template/egpaper_for_review.tex
masters

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
%\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

@@

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

@@

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
   information. Use the word ``Abstract'' as the title, in 12-point
   Times, boldface type, centered relative to the column, initially
   capitalized. The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous 3DIMPVT/3DIM/3DPVT abstracts to get a feel for style and length.
\end{abstract}

@@

%-------------------------------------------------------------------------
\subsection{Language}

@@

By submitting a manuscript to 3DIMPVT, the authors assert that it has not been
previously published in substantially similar form. Furthermore, no paper
which contains significant overlap with the contributions of this paper
either has been or will be submitted during the 3DIMPVT 2012 review period to
{\bf either a journal} or any conference or any
workshop.
 {\bf Papers violating this condition will be rejected and a list of violating authors may be included in the proceedings.}

@@

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document using a non-\LaTeX\
document preparation system, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
the \verb'\cvprfinalcopy' command in the document preamble.)  Reviewers:
note that the ruler measurements do not align well with lines in the paper
--- this turns out to be very difficult to do well when the paper contains
many figures and equations, and, when done, looks ugly.  Just use fractional
references (e.g.\ this line is $095.5$), although in most cases one would
expect that the approximate location will be adequate.

@@

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.  Just
because you didn't refer to it in the text doesn't mean some future reader
might not need to refer to it.  It is cumbersome to have to use
circumlocutions like ``the equation second from the top of page 3 column
1''.  (Note that the ruler will not be present in the final copy, so is not
an alternative to equation numbers).  All authors will benefit from reading
Mermin's description of how to write mathematics.%: \url{http://www.cvpr.org/doc/mermin.pdf}.

@@

Sometimes your paper is about a problem which you tested using a tool which
is widely known to be restricted to a single institution.  For example,
let's say it's 1969, you have solved a key problem on the Apollo lander,
and you believe that the 3DIMPVT12 audience would like to hear about your
solution.  The work is a development of your celebrated 1968 paper entitled
``Zero-g frobnication: How being the only people in the world with access to
the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

@@

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

@@

%------------------------------------------------------------------------
\section{Formatting your paper}

@@

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
high.  Page numbers should be in footer with page numbers, centered and .75
inches from the bottom of the page and make it start at the correct page
number rather than the 4321 in the example.  To do this fine the line (around
line 23)  
\begin{verbatim}
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\end{verbatim}
where the number 4321 is your assigned starting page.

Make sure the first page is numbered by commenting out the first page being
empty on line 46
\begin{verbatim}
%\thispagestyle{empty}
\end{verbatim}

%-------------------------------------------------------------------------
\subsection{Type-style and fonts}

@@

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
should be Times 12-point boldface, initially capitalized, flush left,
with one blank line before.

@@

%-------------------------------------------------------------------------
\subsection{Footnotes}

@@

%-------------------------------------------------------------------------
\subsection{References}

@@

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

@@

%-------------------------------------------------------------------------
\subsection{Color}

@@

%------------------------------------------------------------------------
\section{Final copy}

@@

>>>>

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

@@

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

@@

\author{First Author\\
  Institution1\\
  Institution1 address\\
  {\tt\small firstauthor@i1.org}
  % For a paper whose authors are all at the same institution, omit
  % the following lines up until the closing ``}''.  Additional
  % authors and addresses can be added with ``\and'', just like the
  % second author.  To save space, use either the email address or
  % home page, not both
  \and
  Second Author\\
  Institution2\\
  First line of institution2 address\\
  {\small\url{http://www.author.org/~second}} }

\maketitle
% \thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
  abcd The ABSTRACT is to be in fully-justified italicized text, at the top
  of the left-hand column, below the author and affiliation
  information. Use the word ``Abstract'' as the title, in 12-point
  Times, boldface type, centered relative to the column, initially
  capitalized. The abstract is to be in 10-point, single-spaced type.
  Leave two blank lines after the Abstract, then begin the main text.
  Look at previous 3DIMPVT/3DIM/3DPVT abstracts to get a feel for
  style and length.
\end{abstract}

@@

% -------------------------------------------------------------------------
\subsection{Language}

@@

By submitting a manuscript to 3DIMPVT, the authors assert that it has
not been previously published in substantially similar
form. Furthermore, no paper which contains significant overlap with
the contributions of this paper either has been or will be submitted
during the 3DIMPVT 2012 review period to {\bf either a journal} or any
conference or any workshop.  {\bf Papers violating this condition will
  be rejected}.

@@

% -------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in
the version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document using a non-\LaTeX\
document preparation system, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the
ruler should not change the appearance of any other content on the
page.  The camera ready copy should not contain a ruler. (\LaTeX\
users may uncomment the \verb'\cvprfinalcopy' command in the document
preamble.)  Reviewers: note that the ruler measurements do not align
well with lines in the paper --- this turns out to be very difficult
to do well when the paper contains many figures and equations, and,
when done, looks ugly.  Just use fractional references (e.g.\ this
line is $097.15$), although in most cases one would expect that the
approximate location will be adequate.

@@

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.
Just because you didn't refer to it in the text doesn't mean some
future reader might not need to refer to it.  It is cumbersome to have
to use circumlocutions like ``the equation second from the top of page
3 column 1''.  (Note that the ruler will not be present in the final
copy, so is not an alternative to equation numbers).  All authors will
benefit from reading Mermin's description of how to write mathematics:
\url{http://www.cvpr.org/doc/mermin.pdf}.

@@

Sometimes your paper is about a problem which you tested using a tool
which is widely known to be restricted to a single institution.  For
example, let's say it's 1969, you have solved a key problem on the
Apollo lander, and you believe that the CVPR70 audience would like to
hear about your solution.  The work is a development of your
celebrated 1968 paper entitled ``Zero-g frobnication: How being the
only people in the world with access to the Apollo lander source code
makes us a wow at parties'', by Zeus \etal.

@@

\begin{figure}[t]
  \begin{center}
    \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
    % \includegraphics[width=0.8\linewidth]{egfigure.eps}
  \end{center}
  \caption{Example of caption.  It is set in Roman so that mathematics
    (always set in Roman: $B \sin A = A \sin B$) may be included
    without an ugly clash.}
  \label{fig:long}
  \label{fig:onecol}
\end{figure}

@@

% ------------------------------------------------------------------------
\section{Formatting your paper}

@@

% -------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must
be kept within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8
inches (22.54 cm) high.

% -------------------------------------------------------------------------
\subsection{Type-style and fonts}

@@

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
should be Times 12-point boldface, initially capitalized, flush left,
with one blank line before, and one blank line after.

@@

% -------------------------------------------------------------------------
\subsection{Footnotes}

@@

% -------------------------------------------------------------------------
\subsection{References}

@@

% -------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

@@

% -------------------------------------------------------------------------
\subsection{Color}

@@

% ------------------------------------------------------------------------
\section{Final copy}

@@

% Please direct any questions to the production editor in charge of
% these proceedings at the IEEE Computer Society Press: Phone (714)
% 821-8380, or Fax (714) 761-1784.
